---
title:"EDRM718 Assignment#9"
Author:"Katy Linich, Michael Hornsby and Ruiqin Gao"
Date:"04/11/2020"
output: html_notebook
---
This is a study of the relationship of Post-traumatic stress discorder(PTSD) and childhood sexual abuse (CSA). We want to know if there is a difference in average PTSD of children of different childhood sexual abuse status after adjusting for Childhood physical abuse (CPA) score.
```{r include=FALSE}
library(tidyverse)
library(here)
sexabuse<-read.csv(here("Data", "Abuse.csv"))
sexabuse

```
###Question 1
```{r}
ggplot(data = sexabuse,aes(x=csa, y=ptsd))+
  labs(x=" Childhood sexual abuse status (CSA)",
       y="Post-traumatic stress disorder score (PTSD) ")+
  geom_boxplot(color="red")+
  ggtitle("PTSD score by CSA")
```
###Question 2 Let's get descriptive statistics of ptsd by csa
```{r}
dstat_ptsd<-tapply(sexabuse$ptsd,sexabuse$csa, summary)
dstat_ptsd
SD_ptsd<-tapply(sexabuse$ptsd,sexabuse$csa, sd)
SD_ptsd
```
### Question 3 Let's create side-by-side boxpolot for cas abd cpa
```{r}
ggplot(data = sexabuse,aes(x=csa, y=cpa))+
  labs(x=" Childhood sexual abuse status (CSA)",
       y="Childhood physical abuse score (CPA) ")+
  geom_boxplot(color= "blue")+
  ggtitle("CPA score  by CSA")
```
#4 Let's get descriptive statistics of cpa by csa
```{r}
dstat_cpa<-tapply(sexabuse$cpa,sexabuse$csa, summary)
dstat_cpa
dstat_sd<-tapply(sexabuse$cpa,sexabuse$csa, sd)
dstat_sd
```

#5 Model the response variable as a function of the explanatory variable, the covariate andthe interaction of these variables and test the interaction to confirm that there is notmuch evidence of an interaction.

Response variable- PTSD
Explanatory variable- Childhood sexual abuse

```{r}
ptsd_csa_model <- lm(sexabuse$ptsd~sexabuse$csa*sexabuse$cpa)
anova(ptsd_csa_model)
```



